\chapter*{Acknowledgment}
\vspace{1.0in}
I take this opportunity to express my solemn gratitude and esteemed regards to my thesis guide  
{\bf Prof. Amey Karkare}, for his invaluable help and guidance 
throughout this work, giving me his insights whenever I was 
stuck, motivating me at times when I needed it at most and 
above all for being a kind person.\\
%\\
I wish to thank my thesis co-guide {\bf Prof. Sanjeev K. Aggarwal}, for his 
immense support and invaluable suggestions 
that I have received from him. \\
%\\
I would also like to thank {\bf Prof. Subhajit Roy} for 
all the enriching discussions that I had with him.\\
%\\
In the preparation of this report, I had to consult constantly 
various papers, articles and journals. I, hereby, acknowledge 
my indebtedness to them all. \\
%\\
Special thanks to my friend and fellow mate Sandeep Dasgupta for his encouragement and enormous 
help and lots of thanks to my institution without which this 
thesis would have been a distant reality. \\
%\\
Finally, I wish to extend my thanks to my parents, my sister and my beloved 
friend Debmalya who have always been a source of inspiration 
and encouragement. Their love and blessings have always 
been a driving force in my life to carry all my works 
with hope and optimism.\\
%\\
Every effort has been made to give credit where it is due for
the material contained here in. If inadvertently I have
omitted giving credit to anyone, I apologize and express my
gratitude for their contribution to this work. 
\\
\begin{flushright} \large
\textit{Barnali Basak}\\
\textit{May 2011}\\
\textit{Indian Institute of Technology, Kanpur}\\
\end{flushright}
\newpage
