\documentclass[11pt]{exam}
\usepackage{listings}
\lstset{numbers=left, numberstyle=\tiny, tabsize=2, numbersep=5pt, captionpos=b,
basicstyle=\footnotesize, showstringspaces=false,
emphstyle=\color{LightMagenta}\bfseries, language=Java, frame=single}

\usepackage{color} 
\definecolor{LightMagenta}{cmyk}{0.1,0.8,0,0.1}

\usepackage{enumerate}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=blue
}
\usepackage{multicol}
% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

\ifpdf 
\usepackage{subfigure} 
\usepackage[pdftex]{graphicx} \else 
\usepackage{graphicx} \fi

%  Update these values for running headers
\headrule \lhead[CS 427]{CS427 (Continued)} \chead{\textbf{Final Exam}}
\rhead{netid: \hbox to 0.75 in{}}

\footrule \lfoot{} \cfoot{Page \thepage\ of \numpages} \rfoot{\iflastpage{End of
exam.}{Please go on to the next page\ldots}}

% Add the total points in the exam
\addpoints \boxedpoints \pointsinmargin

% Change the layout of the solution
\renewcommand{\solutiontitle}{
\noindent\textbf{Solution:}\par
\noindent}

\newcommand{\Noo}[1]{}
\newcommand{\Maybe}[1]{}
\newcommand{\Comment}[1]{}
\newcommand{\Ch}[1]{Chapter #1 of Code Complete~2}
\newcommand{\Book}[1]{Chapter #1 of the book \emph{Object-Oriented 
Reengineering Patterns (OORP)}}
\newcommand{\CodeIn}[1]{\begin{small}\texttt{#1}\end{small}}
\newcommand{\ClassMethod}[2]{\CodeIn{#1.#2}} % you can replace . with :: or whatever looks the best in the end
\newcommand{\CodeToDoGeneral}{\CodeToDo{CODE}}
\newcommand{\AnswerToDoGeneral}{\CodeToDo{ANSWER}}
\newcommand{\CodeToDo}[1]{\CodeIn{\textbf{// [TODO] WRITE YOUR #1 BELOW}}}
\newcommand{\CodeInstruction}[1]{\textbf{Write #1 in the space provided underneath the comment in the code below.}}

\newcommand{\CircleAll}{(Circle \textbf{ALL} that apply.)}
\newcommand{\CircleOne}{(Circle \textbf{One} that applies.)}

\newcommand{\QuestionTitle}[1]{\textsc{#1}}
%\widowpenalties 1 10000
%\raggedbottom

\newcommand{\Refactoring}[1]{\textsc{#1}}
\newcommand{\IntroduceParameterObject}{\Refactoring{Introduce Parameter Object}}
\newcommand{\DuplicatedCode}{\Refactoring{Duplicated Code}}

\newcommand{\Choose}[2]{Circle \textbf{one} of \textbf{#1} or
\textbf{#2} and answer the following.}

\begin{document}

\lstset{language=Java,numbers=none,tabsize=4,escapeinside={\%*}{*)}}  \begin{coverpages}
\coverheader{}{\Large \textbf{University of Illinois at
Urbana-Champaign\\Department of Computer Science}}{} \begin{center}
{\Large\textbf{Final Exam}}

 \vspace{0.1 in}

CS 427: Software Engineering I\\ Fall 2013

 \vspace{0.1 in}

December 18, 2013

 \vspace{0.1 in}

TIME LIMIT = 3 Hours \\ COVER PAGE + \numpages\ PAGES \end{center}

 \noindent Write your name and netid neatly in the space provided below; \textbf{write
your netid} in the upper right corner of \textbf{every page}.

 \vspace{0.1 in}

 \hbox to 3 in{Name:\enspace\hrulefill} \hbox to 3 in{Netid:\enspace\hrulefill}

 \vspace{0.1 in}

 \noindent \emph{This is a closed book, closed notes examination. You may not
use calculators or any other electronic devices. Any sort of cheating on the
examination will result in a zero grade.}

 \vspace{0.1 in}

 \noindent \textbf{We cannot give any clarifications about the exam questions
during the test}. If you are unsure of the meaning of a specific question, write
down your assumptions and proceed to answer the question on that basis.

 \vspace{0.1 in}

 \noindent Do all the problems in this booklet. Do your work inside this
booklet, using the backs of pages if needed. The problems are of varying degrees
of difficulty so please pace yourself carefully, and answer the questions in the
order which best suits you. \textbf{Answers to essay-type questions should be as brief
as possible.} If the grader cannot understand your handwriting, you will get 0
points.

 \vspace{0.1 in}

 \noindent There are \numquestions\ questions on this exam and the maximum grade
on this exam is \numpoints\ points.

 \vspace{0.2 in}

	\begin{multicols*}{2}
		\begin{center}			
		\partialgradetable{firsttable}[v][pages] 
		\end{center}
		
		\begin{center}			
		\partialgradetable{secondtable}[v][pages] 
		\end{center}
	\end{multicols*}
	 

\end{coverpages}

% Questions start here:
\begin{questions}

\include{a}
\include{b}
\include{c}
\include{d}

\newcommand{\Coding}[1]{#1}

\newpage
\begingradingrange{firsttable} 
\XP{}
\newpage
\SQA{}
\Advocacy{}
\newpage
\Mistakes{}
\newpage
\OOMetrics{}
\newpage
\Reuse{}
\Testing{}
\newpage
\Coding{\TestingXiaoyu{}}
%\newpage
\ReverseEngineering{}
\CodeSmells{}
\endgradingrange{firsttable}
\newpage
\begingradingrange{secondtable} 
\Coding{\IPO{}}
%\Coding{\RDC{}}
\newpage
\Jenkins{}
\VersionControl{}
\newpage
\Documentation{}
\Patterns{}
\newpage
\Coding{\Iterators{}}
\Coding{\Visitor{}}
%\Coding{\Observer{}}
\endgradingrange{secondtable}
\end{questions}
\end{document}

% LocalWords:  tabsize Urbana Champaign netid eXtreme XP MP4 3x5 refactorings
% LocalWords:  refactoring doesn MPs MP1 JUnit MP2 CodingTracker cs225 boolean
% LocalWords:  newElement PDF IDEs gedit lookup APIs IDE SCM dummied API MP3 OO
% LocalWords:  resequenced reengineering unbundle javadoc codebase refactor txt
% LocalWords:  saveLibrary loadLibrary LibraryTest createLibrary loadedLibrary
% LocalWords:  saveLibraryToFile assertEquals fileName escapeinside
% LocalWords:  firsttable secondtable
