\chapter*{Acknowledgment}
\vspace{1.0in}
I would like to express my heartiest gratitude towards my thesis supervisor {\bf Professor Amey Karkare}
 for his invaluable support and encouragement. His guidance has helped
me from initial till the final level of this work on the way developing a sound
understanding of the topic. It would have been very difficult for me to complete
this work without his innumerable innovative suggestions, the freedom that he has
provided and his utmost patience in hearing my problems out. Apart from gaining a lot from 
his huge technical expertise, starting from gaining tips about how to write a good report to 
getting insights whenever I got struck, I got many learnings which I will explore throughout my life. \\
%%
I wish to thank {\bf Prof. Sanjeev K. Aggarwal}, for his 
immense support and invaluable suggestions 
that I have received from him. \\
I would also like to thank {\bf Prof. Subhajit Roy} for 
all the enriching discussions that I had with him.\\
%%
%In the preparation of this report, I had to consult constantly 
%various papers, articles and journals. I, hereby, acknowledge 
%my indebtedness to them all. \\
%%
Special thanks to my friend and fellow mate 
{\bf Ms. Barnali Basak} for her encouragement and enormous 
help and lots of thanks to my institution without which this 
thesis would have been a distant reality. \\
%%
Finally, I wish to extend my thanks to my parents, my sister and my beloved 
friends, who have always been a source of inspiration 
and encouragement. Their love and blessings have always 
been a driving force in my life to carry all my works 
with hope and optimism.\\
%%
Every effort has been made to give credit where it is due for
the material contained here in. If inadvertently I have
omitted giving credit to anyone, I apologize and express my
gratitude for their contribution to this work. 
\begin{flushright} \large
\textit{Sandeep Dasgupta}\\
\textit{June 2011}\\
\textit{Indian Institute of Technology, Kanpur}\\
\end{flushright}
\newpage
