%\chapter{Comparison with Field Insensitive Approach}\label{ch:Comparison}
\chapter{Comparison with Other Approaches}\label{ch:Comparison}

For comparison purpose the test-cases must involve shape
transitions like Cycle to DAG, Cycle to Tree, and DAG to
Tree. The transition like Tree to DAG, DAG to Cycle, or Tree
to Cycle are not of much importance as these can be detected
by any of the field insensitive approaches. Following are the
cases that meet our requirement and better demonstrate the
accuracy of our analysis as compared to field insensitive
analysis (like Ghiya et. al.~\cite{Ghiya96}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with Ghiya et. al.~\cite{Ghiya96}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\nO}{\mbox{\tt n1}}
\newcommand{\nT}{\mbox{\tt n2}}
\newcommand{\myt}{\mbox{\tt t}}
\newcommand{\T}{\mbox{\tt T}}
\newcommand{\myL}{\mbox{\tt L}}
\newcommand{\R}{\mbox{\tt R}}

\input{test_1.tex}
\input{test_2.tex}
\input{test_3.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with Marron et. al.~\cite{marron06static}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Using the property as mentioned in Appendix B, we inferred the shape of the data structure corresponding to 
each region for the test-cases that we have chosen, and concluded that their shape inferencing comply exactly with the actual
shapes that should be reported.

To eliminate the state explosion that is possible with refinement, they apply refinement to only those 
cases where there exist a unique way of materializing new nodes. This limits the amount of precision 
that can be achieved as there exists cases where refinement into  multiple possibilities is needed to get results with the
desired accuracy.    
